Model Building

### 2020-08-03 Model_Build.Rmd
Added interpretations for arima model and added hierarchical model

# creating snaive, ets, and arima models
fit <- lad %>%
  model(
    arima = ARIMA(googlehits ~ odds + attgame + winpct) # testing with only arima right now
  )

@@

>>>>

# creating arima models
fit <- lad %>%
  model(
    arima = ARIMA(googlehits ~ odds + attgame + winpct + payroll + DivWin + LgWin + WSWin) # testing with only some regressors
  )

@@

## Interpretting Time Series Terms
### Dodger Example

ARIMA(p,d,q)(P,D,Q)s

In this case focusing on just the Dodgers, we have an $ARIMA(0,0,0)(1,0,1)12$ model. The $12$ represents the numer of periods within a year; therefore, this is a monthly series. The seasonal autoregressive order 1 (sar1) term means that we are using a linear combination with the values of the variable of interest, google hits, lagged from exactly 12 months ago.  The seasonal moving average order 1 (sma1) means that the current google hits are affected by some random error from exactly 12 months ago.

The model without the exogenous regressors can be written as by $(Y_t-\phi_{12} Y_{t - 12}) = (e_{t}+\Theta_{12} e_{t-12})$  where $\phi_{12} = 0.509$ and $\Theta_{12} = 0.308$. This $0.308$ of the sar1 term can interpretted as moving $60.2\%$ of the way from the current google hits toward the average of the google hits.  The $0.509$ of the

I'm iffy on the numerical interpretations of these terms ^. Most people say that they are just different weights and either converge or diverge faster or slower depending on the estimate of the coefficient.

## Hierarchial Model
```{r}
# all I did was add propTVMarketSize as a key when converting to tsibble, not sure if that's the correct way to do it? I didn't add propTVMarketSize to the arima model.  It says it wasn't found if I add it there.

alldata_hier <- combined %>%
  rename(attendance = attendance.x) %>%
  select(-c(year, attendance.y)) %>%
  mutate(date = yearmonth(date)) %>%
  as_tsibble(key = c(team, propTVMarketSize), index = date)

hier_model <- alldata_hier %>%
  model(
    arima = ARIMA(googlehits ~ odds + attgame + winpct + payroll + DivWin + LgWin + WSWin)
  )

hier_fitted <- augment(hier_model)

hier_model %>%
  select(team, arima) %>%
  coef()
```
